Just getting started 
  Getting the spacers right when attaching a spectrograph
  Finding your target
  What stars can I observe with my spectrograph
  Focusing a spectrograph – Temperature excursions
  Autoguiding
  Calibration
  How long of an exposure should I take?
  How many exposures should I take? (odd number)

How to take Calibration images
  SA100/SA200

What is resolution?

What is a 1D and a 2D fits file? 

Engineering 
  What do you do if you take the instrument off an put it back on
  How to I align my slit
  What slit width should I use and why
  Measuring deflection at different points in the sky using Cal lamp

Order overlap
  Processing spectral data 

Which spectral processing software should I use?  
  Why we use ISIS?
  How to we name files and how do we organize file storage.

Important Fits key words
  Cosmic Ray reduction and impact.
  How do we make Master calibration images?
  Do we do darks or not and why

How to configure ISIS
  How to process spectral data in ISIS

Why should I use a Reference star and how to Select one?

Instrument and Response calibration

Robin Leadbeater - BAA Low Resolution Slit Spectroscopy
Checking your spectra with that produced by others

 Projects

--Wayne's Demos:

   Light Pollution - Wayne
   Site location qualification – Wayne
   Telluric lines by season – Wayne
   Shoot the blue sky – Wayne
   Novae, Nova Del 2013 – Wayne
   Using the bright emission features of the Orion Nebula as a rough
   guide to where lines are in your spectra - Wayne

Shoot a Miles reference star and compare the real Miles spectra
Bess stars
Symbiotic stars


Show and Tell


Phi Per Ha LHiresIII  - Al Stiewing
David star LHiresIII – Ken Hudson
Pleiades double star – Bob and Woody
Light pollution test results

Spectral typing

Identifying spectral features – P Cygni, element identification

Stellar classification work with Alpy -Bob

3 belt stars of Orion – Al Stiewing

Betelgeuse – expanding shell star



Planets – Jupiter

Solar spectra of sky vs the Moon

Time series of stellar spectra

Relco vs GE lamp – Clarke Yaeger


Examples of amateur spectrographs SA100/SA200, Alpy, 
    LISA, L200, SHiresIII, UVEX and Eschelle


Advanced topics
   Atmospheric extinction - Wayne
   Parallactic Angle data set – Woody
   Average vs median combing spectral data – Wayne
   Equivalent Widths
   Flux calibration
   Normalization/rectification of spectrum


Software
   Aladin
   DS9
   Topcat
   Glue viz.org
   Fitsverify – NASA
   Vspec
   IRaf

Reference Area

 Github repository - Wayne
    If you find something useful to this group we will get it 
    upstairs for shared access.

 Where to submit spectral data
   ARAS
   Bess
   BAA
   AAVSO
   Tricks

